Open, privacy-preserving protocols for lawful surveillance

### 2016-04-14 rebuttal.txt

Reviewers C and D seem to base their "reject" scores on the notion that
section 3 is our main contribution. Actually, section 3 is intended as
relevant background from our previous paper. Sections 4 and 5 are our
main results, as reviewer A noted. A camera-ready version without
author anonymity requirements would make this relationship clear.

Section 3.3 is indeed merely an engineering result, which we never
intended to carry the weight of the paper. We included it in order to
respond to specific concerns raised after the presentation of our last
paper. It could be moved to an appendix.

Reviewer A:

We selected the social network to experiment on because we preferred
real data to simulated data, and because the actual phone call graph is
not freely available. But we do have similar results for simulated
graphs which we could include in the camera-ready version.

Reviewer B:

If the law enforcement agency already holds part of the database, we
can treat that agency as a "telecom" for the purpose of the protocol
without (further) compromising privacy.

Our understanding is that the changes to the "215" program mean that
the telecoms store user data until it is searched by the government.
Although we did not say so explicitly, that is the model our
contact-chaining algorithm uses.

Reviewer C:

It is true that telecoms have colluded with law enforcement in the
past, but no system can account for telecoms arbitrarily sending data
to other parties, except perhaps for a legal evidentiary hearing.

Reviewer D:

We agree that a solution resistant to all agencies colluding would be
excellent, but the notion of distributed trust is also well-founded in
the literature. On the other hand, neither of the alternatives reviewer
D mentions serve for the purpose of mass surveillance that we address,
and neither of them have considered contact-chaining, our main
contribution.

We are familiar with accountable anonymity, but the problem of mass
surveillance is fundamentally different. Accountable anonymity treats
each user as a party to the protocol. In papers such as Tsang et al.,
"revoked" users are not deanonymized, and the authority responsible for
revoking users is assumed to be honest. In dining-cryptographers-based
accountable anonymity protocols, the identities of all users must be
known in advance, and individual users can be held accountable only
through a deviation from the protocol in some way, and potentially at
great computational cost. Neither type of accountable anonymity is
fully collusion-resistant.

Revokable privacy is similar to privacy-preserving surveillance in many
ways, but the crucial distinction is that revokable privacy has been
studied primarily in theoretical contexts involving fairly small
amounts of data, whereas our work focuses on practicality, scalability,
and *mass* surveillance. Lueks et al. offer no sense of how long it
would take to run forward-secure distributed encryption on commercial
hardware, and their protocols are exponential. The common use case of
hundreds of cars driving down a highway is not scalable to hundreds of
thousands (or more) of users on a communication network.

### 2016-07-12 paper/conc.tex
More-or-less revised for arXiv preprint submission. Bibliography is a terrible mess though.

>>>>

\subsection*{Acknowledgments}

The first author was supported by a Google Faculty Research Award.
The second author was supported by NSF grants CNS-1407454 and CNS-1409599, DHS grant FA8750-16-2-0034, and William and Flora Hewlett Foundation grant 2016-3834.
The third author was supported by EPFL, the AXA Research Fund, and DHS grant FA8750-16-2-0034.

### 2016-07-12 paper/intro.tex
More-or-less revised for arXiv preprint submission. Bibliography is a terrible mess though.

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014}\footnote{Throughout this submission, we
cite an anonymized version of an existing paper on accountable surveillance
and use the pseudonym ``Bandits'' instead of the names of the authors.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

>>>>

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014},
%\footnote{Throughout this submission, we
%cite an anonymized version of an existing paper on accountable surveillance
%and use the pseudonym ``Bandits'' instead of the names of the authors.}
we seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

### 2016-07-12 paper/submission.tex
More-or-less revised for arXiv preprint submission. Bibliography is a terrible mess though.

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{etex}
\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
\usepackage[big]{dgruyter_NEW}

\DOI{foobar}

\cclogo{\includegraphics{by-nc-nd.pdf}}

@@

  %\author*[1]{Aaron Segal}
  \author[1]{Names withheld}

@@

  %\affil[1]{Yale Univ., E-mail: Aaron.Segal@yale.edu}
  \affil[1]{Affiliations and email addresses withheld}

@@

  \title{\huge Open, privacy-preserving protocols for lawful surveillance}

  \runningtitle{Privacy-preserving, lawful surveillance}

@@

  \begin{abstract}
{The question of how government agencies can
acquire actionable, useful information about legitimate but unknown targets 
without intruding upon the electronic activity of innocent parties is 
extremely important.  We address this question by providing experimental
evidence that actionable, useful information can indeed be obtained in a manner
that preserves the privacy of innocent parties and that holds government
agencies accountable.  In particular, we present practical, privacy-preserving
protocols for two operations that law-enforcement and intelligence agencies
have used effectively: {\it set intersection} and {\it contact chaining}.
Experiments with our protocols suggest
that privacy-preserving contact chaining can perform
a 3-hop privacy-preserving graph traversal producing 27,000 ciphertexts
in under two minutes.
These ciphertexts are usable in turn via privacy-preserving set
intersection to pinpoint potential unknown targets within a body of 150,000
total ciphertexts within 10 minutes,
without exposing personal information about non-targets.
}
  \end{abstract}
  \keywords{Privacy, Secure multiparty computation, Surveillance}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

  \journalname{Proceedings on Privacy Enhancing Technologies}
\DOI{Editor to enter DOI}
  \startpage{1}
  \received{February 29, 2016}
  %\revised{..}
  %\accepted{..}

  \journalyear{2016}
  \journalvolume{2016}
  \journalissue{4}

@@

%\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
%In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
%Open Communications on the Internet, August 18, 2014, San Diego, 
%USA (USENIX, Berkeley, 2014)

@@

\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
Privacy-Preserving Intersection Warrants for Lawful Surveillance,
February 2016, \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}

>>>>

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{etex}
\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
%\usepackage[big]{dgruyter_NEW}
\usepackage{amsmath}
\usepackage{hyperref}

%\DOI{foobar}

%\cclogo{\includegraphics{by-nc-nd.pdf}}

@@

  \title{Open, privacy-preserving protocols for lawful surveillance}
  \author{
	Aaron Segal and Joan Feigenbaum \\
	Yale University \\
	New Haven, CT, USA
	\and
	Bryan Ford \\
	Swiss Federal Institute of Technology (EPFL) \\
	Lausanne, Switzerland}
  \date{}

  %\author*[1]{Aaron Segal}
  %\author[1]{Names withheld}

@@

  %\affil[1]{Yale Univ., E-mail: Aaron.Segal@yale.edu}
  %\affil[1]{Affiliations and email addresses withheld}

@@

  %\title{\huge Open, privacy-preserving protocols for lawful surveillance}

  %\runningtitle{Privacy-preserving, lawful surveillance}

@@

  \begin{abstract}
{The question of how government agencies can
acquire actionable, useful information about legitimate but unknown targets 
without intruding upon the electronic activity of innocent parties is 
extremely important.  We address this question by providing experimental
evidence that actionable, useful information can indeed be obtained in a manner
that preserves the privacy of innocent parties and that holds government
agencies accountable.  In particular, we present practical, privacy-preserving
protocols for two operations that law-enforcement and intelligence agencies
have used effectively: {\it set intersection} and {\it contact chaining}.
Experiments with our protocols suggest
that privacy-preserving contact chaining can perform
a 3-hop privacy-preserving graph traversal producing 27,000 ciphertexts
in under two minutes.
These ciphertexts are usable in turn via privacy-preserving set
intersection to pinpoint potential unknown targets within a body of 150,000
total ciphertexts within 10 minutes,
without exposing personal information about non-targets.
}
  \end{abstract}
%  \keywords{Privacy, Secure multiparty computation, Surveillance}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

  %\journalname{Proceedings on Privacy Enhancing Technologies}
  %\DOI{Editor to enter DOI}
  %\startpage{1}
  %\received{February 29, 2016}
  %\revised{..}
  %\accepted{..}

  %\journalyear{2016}
  %\journalvolume{2016}
  %\journalissue{4}

@@

\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
Open Communications on the Internet, August 18, 2014, San Diego, 
USA (USENIX, Berkeley, 2014)

@@

%\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
%Privacy-Preserving Intersection Warrants for Lawful Surveillance,
%February 2016, \url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
